### 2020-02-11 README.Rmd
summarize_oolong is ready, fix #6. First minor version.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

As instructed, use the method `$do_word_intrusion_test()` to start coding. If you are running this in RStudio, you should see a test screen similar to this:

@@

```{r, eval = FALSE}
oolong_test$lock()
oolong_test
```

@@

```{r, eval = FALSE}
oolong_test$lock()
oolong_test
```

@@

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
set.seed(42)
```

@@

As instructed, use the method `$do_word_intrusion_test()` to start coding.

```{r, eval = FALSE}
oolong_test$do_word_intrusion_test()
```

If you are running this in RStudio, you should see a test screen similar to this:

@@

```{r, include = FALSE}
### Mock this process
oolong_test$.__enclos_env__$private$test_content$word$answer <- oolong_test$.__enclos_env__$private$test_content$word$intruder
oolong_test$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
```

```{r lock}
oolong_test$lock()
oolong_test
```

@@

```{r, eval = FALSE}
oolong_test$do_topic_intrusion_test()
oolong_test$lock()
```

```{r, include = FALSE}
genius_topic <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
    return(obj1)
}
genius_word <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
    return(obj1)
}
oolong_test <- genius_word(genius_topic(oolong_test))
oolong_test$.__enclos_env__$private$test_content$topic$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$topic$candidates[[2]], 1)
oolong_test$lock()
```

```{r topic_res}
oolong_test
```

@@

Train a topic model.

```{r step0, eval = FALSE}
require(quanteda)
require(stm)
dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
docvars(newsgroup5_dfm, "title") <- newsgroup5$title
newsgroup5_dfm %>% convert(to = "stm", omit_empty = FALSE) -> newsgroup5_stm
newsgroup_stm <- stm(newsgroup5_stm$documents, newsgroup5_stm$vocab, data =newsgroup5_stm$meta, K = 10, seed = 42)
```
